---
title: "Mad Lib Mother Goose"
author: "Sujata Emani"
date: "August 2, 2018"
font-family: 'Times'
output: html_document
#output: slidy_presentation: incremental = true
runtime: shiny
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
***
## Shiny Project: MadLib Mother Goose

According to Wikipedia Mad Libs are: _a phrasal template word game where one player prompts others for a list of words to substitute for blanks in a story, before reading the - often comical or nonsensical - story aloud. The game is frequently played as a party game or as a pastime._

Here we can enjoy a few Mad Libs with a Mother Goose poem. You won't know the poem of course until you play with the application. 

***
## The Goal

The Goal of this Project is multi-fold.
    1.  Write a Shiny App
    2.  Utilize Shiny Widgets
    3.  Employ Reactive functions
    4.  Deploy the app on the RStudio Shiny server
    5.  Create Slides to explain the Shiny app

***    
## The Code Segments: ui 

```{r The Code, echo = TRUE, eval = FALSE, strip.white= TRUE}
library(shiny)
source("madlibRhyme.R")

ui <- fluidPage(
        titlePanel("MadLib Nursery Rhymes"),
        sidebarLayout(
            sidebarPanel(
                helpText("MadLibs are funny stories or poems formed 
                        when you supply various words of different
                        parts of speech without knowing what the 
                        story is before hand."),
                selectInput("select", label = h4("Select which Rhyme"),
                            choices = list ("Rhyme 1", "Rhyme 2", "Rhyme 3"),
                            selected = "Rhyme 1"),
                
                textInput(inputId = "noun1", label = NULL, value = "Enter a proper Name..."),
                textInput(inputId = "noun2", label = NULL, value = "Enter a place..."),
                textInput(inputId = "noun3", label = NULL, value = "Enter an animal..."),
                textInput(inputId = "adj1", label = NULL, value = "Enter an adjective..."),
                textInput(inputId = "adj2", label = NULL, value = "Enter an adjective..."),
                textInput(inputId = "adj3", label = NULL, value = "Enter an adjective..."),
                textInput(inputId = "verb1", label = NULL, value = "Enter a verb in present tense..."),
                textInput(inputId = "verb2", label = NULL, value = "Enter a verb in past tense..."),
                textInput(inputId = "verb3", label = NULL, value = "Enter a verb in past tense..."),
                helpText("Click \"MadLib!\" to start!"),
                actionButton("goButton", "MadLib!")
            ), 
            mainPanel(
                h2("Your Mother Goose Madlib!"),
                h3(textOutput("text")),
                tags$head(tags$style("#text{color: red;
                                 font-size: 20px;
                                     font-style: italic;
                                     }"
                         )
                )
            )
        )
       
)
```

***
## The Code Segment: server

```{r Code Segment: server, echo=TRUE, eval = FALSE, strip.white=TRUE}
server <- function(input, output) {
    
    output$text <- renderText({
        mlrhymeInput()
    })
    mlrhymeInput <- eventReactive(input$goButton, {
        selectedRhyme <- switch(input$select, 
                                "Rhyme 1" = 1,
                                "Rhyme 2" = 2,
                                "Rhyme 3" = 3)
        madlibVector <- c(input$noun1, input$noun2, input$noun3, input$adj1, input$adj2,
                          input$adj3, input$verb1, input$verb2, input$verb3)
        
        madlibRhyme(selectedRhyme, madlibVector)
    })
}
```

***
## Additional Code Segment: madlibRhyme

```{r Code Segment: madlibRhyme, echo = TRUE, eval = FALSE, strip.white=TRUE}
madlibRhyme <- function(rhymenum, words){
    if(rhymenum == 1){
        Rhyme1 <- paste(words[1],", ", words[1], ", pumpkin eater,", words[8], "a ", words[3], 
                    "and couldn\'t keep her;", words[1], "put her in a ", words[4],
                    " shell, and there ", words[1], " ", words[9], " her very well.")
        return(Rhyme1)
    }
    if(rhymenum == 2){
        Rhyme2 <- paste("There was an ", words[5]," woman who lived in ", words[2], 
                    " had so many ", words[3],"s , she didn't know what to do. She ",
                    words[7], " them some broth without any bread, then ", words[8], 
                    " them all soundly and ", words[9]," them to bed.")
        return(Rhyme2)
    }
    if(rhymenum == 3){
        Rhyme3 <- paste(words[3],", ", words[3], " where have you been?", " I've been to ", 
                    words[2], " to ", words[7], " ", words[1],". ", words[3],", ", words[3], 
                    " what did you do there?", " I ", words[8], " a ", words[6], 
                    " mouse under a chair.")
        return(Rhyme3)
    }
}
```

***
## The Shiny App: Mad Lib Mother Goose

```{r Additional Code, echo = FALSE}
madlibRhyme <- function(rhymenum, words){
    if(rhymenum == 1){
        Rhyme1 <- paste(words[1],", ", words[1], ", pumpkin eater,", words[8], "a ", words[3], 
                    "and couldn\'t keep her;", words[1], "put her in a ", words[4],
                    " shell, and there ", words[1], " ", words[9], " her very well.")
        return(Rhyme1)
    }
    if(rhymenum == 2){
        Rhyme2 <- paste("There was an ", words[5]," woman who lived in ", words[2], 
                    " had so many ", words[3],"s , she didn't know what to do. She ",
                    words[7], "s them some broth without any bread, then ", words[8], 
                    " them all soundly and ", words[9]," them to bed.", sep = "")
        return(Rhyme2)
    }
    if(rhymenum == 3){
        Rhyme3 <- paste(words[3],", ", words[3], " where have you been?", " I've been to ", 
                    words[2], " to ", words[7], " ", words[1],". ", words[3],", ", words[3], 
                    " what did you do there?", " I ", words[8], " a ", words[6], 
                    " mouse under a chair.")
        return(Rhyme3)
    }
}
```

```{r The App: ui, echo = FALSE}
library(shiny)
source("madlibRhyme.R")

ui <- fluidPage(
        titlePanel("MadLib Nursery Rhymes"),
        sidebarLayout(
            sidebarPanel(
                helpText("MadLibs are funny stories or poems formed 
                        when you supply various words of different
                        parts of speech without knowing what the 
                        story is before hand."),
                selectInput("select", label = h4("Select which Rhyme"),
                            choices = list ("Rhyme 1", "Rhyme 2", "Rhyme 3"),
                            selected = "Rhyme 1"),
                
                textInput(inputId = "noun1", label = NULL, value = "Enter a proper Name..."),
                textInput(inputId = "noun2", label = NULL, value = "Enter a place..."),
                textInput(inputId = "noun3", label = NULL, value = "Enter an animal..."),
                textInput(inputId = "adj1", label = NULL, value = "Enter an adjective..."),
                textInput(inputId = "adj2", label = NULL, value = "Enter an adjective..."),
                textInput(inputId = "adj3", label = NULL, value = "Enter an adjective..."),
                textInput(inputId = "verb1", label = NULL, value = "Enter a verb in present tense..."),
                textInput(inputId = "verb2", label = NULL, value = "Enter a verb in past tense..."),
                textInput(inputId = "verb3", label = NULL, value = "Enter a verb in past tense..."),
                helpText("Click \"MadLib!\" to start!"),
                actionButton("goButton", "MadLib!")
            ), 
            mainPanel(
                h2("Your Mother Goose Madlib!"),
                h3(textOutput("text")),
                tags$head(tags$style("#text{color: red;
                                 font-size: 20px;
                                     font-style: italic;
                                     }"
                         )
                )
            )
        )
       
)
```

```{r Server, echo = FALSE}
server <- function(input, output) {
    output$text <- renderText({
        mlrhymeInput()
    })
    mlrhymeInput <- eventReactive(input$goButton, {
        selectedRhyme <- switch(input$select, 
                                "Rhyme 1" = 1,
                                "Rhyme 2" = 2,
                                "Rhyme 3" = 3)
        madlibVector <- c(input$noun1, input$noun2, input$noun3, input$adj1, input$adj2,
                          input$adj3, input$verb1, input$verb2, input$verb3)
        
        madlibRhyme(selectedRhyme, madlibVector)
    })
}
shinyApp(ui = ui, server = server)
```

## Thank you for playing with the Mad Lib Mother Goose application!